\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-27 paper2015asml.tex
fix for highlight
additions, notes

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studied recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a cost-map was developed in conjunction with sampling based planning to produce trajectories in cluttered environments.}

@@

\hl{We would also like to extend our set of features in multiple ways. We would like to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. We would also like to introduce more environment specific features, e.g. the descriptors in~\cite{10-jetchev-ICRA}, to account better for the effect of the environment on the ratings. Context and task specific features would be useful in capturing task specific motions, e.g. a robot turning a screwdriver may actually need to turn its wrist continuously. Incorporating task motions and relevant environments, e.g. picking up an object from a cluttered table, would also help in evaluating features like legibility. We would also like to examine how people's ratings change as they spend more time observing the robot (this effort will require a longer running survey or multiple surveys spaced apart in time). We would also like to include features to encode the choice of start and goal positions for the robot - several of the existing features could easily be adapated to take this into account.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could also easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.

>>>>

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studied recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a costmap was developed for use in motion planning taking into account human interaction constraints like gaze, proximity to the robot and ease of hand-off.}

@@

\hl{We would also like to extend our set of features in multiple ways. We would like to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. We would also like to introduce more environment specific features, e.g. the descriptors in}~\cite{10-jetchev-ICRA}, \hl{to account better for the effect of the environment on the ratings. Context and task specific features would be useful in capturing task specific motions, e.g. a robot turning a screwdriver may actually need to turn its wrist continuously. Incorporating task motions and relevant environments, e.g. picking up an object from a cluttered table, would also help in evaluating features like legibility. We would also like to examine how people's ratings change as they spend more time observing the robot (this effort will require a longer running survey or multiple surveys spaced apart in time). We would also like to include features to encode the choice of start and goal positions for the robot - several of the existing features could easily be adapated to take this into account.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could also easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.
